FAIR fission track analysis with geochron@home

### 2025-10-02 geochron@home/manuscript/paper.tex
Flipped numerator and denominator in grain 1 vs 2 comparison

In spite of the under-counting by the students, the ratio of their
pooled track counts ($r_p$) for two different grains is often close to
PV's ratio, especially when comparing grains with similar track
densities. This is illustrated in Figure~\ref{fig:23vs25}a for
grains~23 and 25.  For any point, the ratio of the two counts is given
by the slope of a line from the origin to that point. Although the
individual slopes vary considerably, the line with slope equal to the
ratio of the total counts for all students (which is 0.96) passes
close to PV's pair of counts (52,50) shown by the blue dot (with ratio
1.03). It is interesting that the students with lower counts are
mostly above this line and those with higher counts are all below it.
There is a positive correlation between the pairs of counts,
consistent with systematic observer effects (i.e., people who count a
low value in one grain tend to count similarly low in the other, and
vice versa). Comparing other pairs of grains shows similar results,
with correlations varying between 0.4 and 0.9.\medskip

\noindent\begin{minipage}{.55\linewidth}
  \includegraphics[width=\linewidth]{stripchart.pdf}\medskip
\end{minipage}
\begin{minipage}{.45\linewidth}
\captionof{figure}{ Dot plot of the data shown in
  Table~\ref{tab:crowdtable}, with the students' medians and PV's
  counts shown as yellow and blue triangles, respectively.
  \medskip}
  \label{fig:stripchart}
\end{minipage}

@@

%\begin{figure}[!ht]
{ \centering \includegraphics[width=15cm]{23vs25.pdf}
  \captionof{figure}{a) The track counts for grain~23 plotted against
    those for grain 25 for 36 students who counted both of those
    grains. The grey line through the origin has slope equal to the
    ratio of the total counts for each grain. The blue dot shows PV's
    counts for those two grains. b) Optical images in transmitted
    light of Mount Dromedary apatites 23 and 25 in the crowd-sourcing
    experiment, along with two-dimensional histogram of the track
    locations for the two grains, as identified by the citizen
    scientists.
    \medskip}
  \label{fig:23vs25}
}%\end{figure}

>>>>

In spite of the under-counting by the students, the ratio of their
pooled track counts ($r_p$) for two different grains is often close to
PV's ratio, especially when comparing grains with similar track
densities. This is illustrated in Figure~\ref{fig:23vs25}a for
grains~23 and 25.  For any point, the ratio of the two counts is given
by the slope of a line from the origin to that point. Although the
individual slopes vary considerably, the line with slope equal to the
ratio of the total counts for all students (which is 0.97) passes
close to PV's pair of counts (52,50) shown by the blue dot (with ratio
1.04). It is interesting that the students with lower counts are
mostly above this line and those with higher counts are all below it.
There is a positive correlation between the pairs of counts,
consistent with systematic observer effects (i.e., people who count a
low value in one grain tend to count similarly low in the other, and
vice versa). Comparing other pairs of grains shows similar results,
with correlations varying between 0.4 and 0.9.\medskip

\noindent\begin{minipage}{.55\linewidth}
  \includegraphics[width=\linewidth]{stripchart.pdf}\medskip
\end{minipage}
\begin{minipage}{.45\linewidth}
\captionof{figure}{Dot plot of the data shown in
  Table~\ref{tab:crowdtable}, with the students' medians and PV's
  counts shown as yellow and blue triangles, respectively.
  \medskip}
  \label{fig:stripchart}
\end{minipage}

@@

%\begin{figure}[!ht]
{ \centering \includegraphics[width=15cm]{23vs25.pdf}
  \captionof{figure}{a) The track counts for grain~23 plotted against
    those for grain 25 for 36 students who counted both of those
    grains. The grey line through the origin has slope 0.97, equal to
    the ratio of the students' total counts for each grain.  The blue
    dot shows PV's counts for those two grains. b) Optical images in
    transmitted light of Mount Dromedary apatites 23 and 25 in the
    crowd-sourcing experiment, along with two-dimensional histogram of
    the track locations for the two grains, as identified by the
    citizen scientists.
    \medskip}
  \label{fig:23vs25}
}%\end{figure}
